\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-30 latex/paper_sensores/paper.tex
ultimas cosas

The first step of the calibration is to obtain the static parameters of the devices for the ambiance temperature. This step is based on knowing the exact orientation of the IMU for the calibration of both sensors and the exact angular speed for the gyroscope calibration. Other related works waive this requirement\cite{bib:calib_imu, bib:kalman} and uses the fact that in any position angular speed (for the gyroscope calibration) and gravity vector (for the accelerometer calibration) are constant.\\

@@

\subsection{Accelerometer}
Due to construction issues the sensitivity axis of the device are generally not orthogonal. Lets define a platform system as shown in Figure \refp{fig:mongoose}. Let $\mathbf{a}^a$ be the true acceleration (meaning the theoretical acceleration measured in $ms^{-2}$) expressed in the sensitivity axis of the accelerometer and let $\mathbf{a}^p$ be the theoretical true acceleration (also measured in $ms^{-2}$) expressed in the platform system. The two acceleration vectors are related according to equation \refp{eq:nonorto}:
\begin{equation}
\mathbf{a}^p = \mathbf{T}_a^p\mathbf{a}^a, \; \mathbf{T}_a^p = \left(\begin{array}{ccc}
1 & - \alpha_{yz} & \alpha_{zy}\\
\alpha_{xz} & 1 & - \alpha_{zx}\\
-\alpha_{xy} & \alpha_{yx} & 1
\end{array}\right)
\label{eq:nonorto}
\end{equation}
In equation \refp{eq:nonorto}, scalars $\alpha_{ij}$ represents the rotation of the $i-th$ sensitivity axis of the accelerometer over the $j-th$ axis of the platform system. In Figure \refp{fig:nonorto} this relation can be observed graphically. Since those errors are due to the manufacturing process we will assume that they will remain constant long enough.

@@

In this work we also propose to implement a temperature adjustment. The sensors are exposed to the operating temperature of the system, and it is very common that this temperature is different from the calibration temperature. Sensors based in MEMS technology are sensitive to such variations. The variation of the measures is critical in some applications (see \cite{bib:uquad} for example). In INS two of the Euler angles are usually obtained from the accelerometer, therefore if the measures are not certain the stability of the system cannot be guaranteed.\\

@@

\begin{itemize}
\item Sensitivity variation of the accelerometer: $\pm 0.01 \%/^\circ C$
\item Offset variation of the accelerometer: $\pm 1.2mg/^\circ C \approx 0.012m s^{-1}$
\item Sensitivity variation of the gyroscope: No information is provided. 
\item Offset variation of the accelerometer: $\pm 40 ^\circ s^{-1} \approx 0.70 rad s^{-1}$
\end{itemize}

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=.8\columnwidth]{./pics_paper/resultado_temp.png}
	\caption{\textbf{Gyroscope setup - }Accelerometer measurement in z-axis vs. temperature while heating up the sensor.}
	\label{fig:resultado_temp}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=.8\columnwidth]{./pics_paper/bajada.png}
	\caption{\textbf{Gyroscope setup - }Accelerometer measurements and temperature (T) vs. time while T varying from $35^oC$ to $48^oC$.}
	\label{fig:bajada}
\end{figure}

>>>>

The first step of the calibration is to obtain the static parameters of the devices for the ambiance temperature. This step is based on knowing the exact orientation of the IMU for the calibration of both sensors and the exact angular speed for the gyroscope calibration. Other related works waive this requirement \cite{bib:calib_imu, bib:kalman} and uses the fact that in any position angular speed (for the gyroscope calibration) and gravity vector (for the accelerometer calibration) are constant.\\

@@

\subsection{Accelerometer}
Due to construction issues the sensitivity axis of the device are generally not orthogonal. Lets define a platform system as shown in Figure \refp{fig:mongoose}. Let $\mathbf{a}^a$ be the true acceleration (meaning the theoretical acceleration measured in $ms^{-2}$) expressed in the sensitivity axis of the accelerometer and let $\mathbf{a}^p$ be the theoretical true acceleration (also measured in $ms^{-2}$) expressed in the platform system. The two acceleration vectors are related according to equation \refp{eq:nonorto}:
\begin{equation}
\mathbf{a}^p = \mathbf{T}_a^p\mathbf{a}^a, \; \mathbf{T}_a^p = \left(\begin{array}{ccc}
1 & - \alpha_{yz} & \alpha_{zy}\\
\alpha_{xz} & 1 & - \alpha_{zx}\\
-\alpha_{xy} & \alpha_{yx} & 1
\end{array}\right)
\label{eq:nonorto}
\end{equation}
In equation \refp{eq:nonorto}, scalars $\alpha_{ij}$ represents the rotation of the $i-th$ sensitivity axis of the accelerometer over the $j-th$ axis of the platform system. In Figure \refp{fig:nonorto}\footnote{Figure taken form \cite{bib:calib_imu}} this relation can be observed graphically. Since those errors are due to the manufacturing process we will assume that they will remain constant long enough.

@@

In this work we also propose to implement a temperature adjustment. The sensors are exposed to the operating temperature of the system, and it is very common that this temperature is different from the calibration temperature. The thermometer used in this work is the internal thermometer of the IMU, which indicates very precisely the operating temperature of the sensor. Sensors based in MEMS technology are sensitive to such variations. The variation of the measures is critical in some applications (see \cite{bib:uquad} for example). In INS two of the Euler angles are usually obtained from the accelerometer, therefore if the measures are not certain the stability of the system cannot be guaranteed.\\

@@

\begin{itemize}
\item Sensitivity variation of the accelerometer: $\pm 0.01 \%/^\circ C$
\item Offset variation of the accelerometer: $\pm 1.2mg/^\circ C \approx 0.012m s^{-1}$
\item Sensitivity variation of the gyroscope: No information is provided. 
\item Offset variation of the gyroscope: $\pm 40 ^\circ s^{-1} \approx 0.70 rad s^{-1}$
\end{itemize}

@@

For the calibration there were used 1934 samples, taken in about 20 seconds.\\

@@

\begin{figure}
	\centering
	\includegraphics[width=.8\columnwidth]{./pics_paper/resultado_temp.png}
	\caption{\textbf{}Accelerometer measurement in z-axis vs. temperature while heating up the sensor.}
	\label{fig:resultado_temp}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=.8\columnwidth]{./pics_paper/bajada.png}
	\caption{\textbf{}Accelerometer measurements and temperature (T) vs. time while T varying from $35^oC$ to $48^oC$.}
	\label{fig:bajada}
\end{figure}
